Competing Bandits:\\The Perils of Exploration under Competition

### 2018-11-05 paper/content/introduction.tex
intro

\swedit{Beyond the welfare implications, we also investigate the barrier to entry that follows from the incumbent's data advantage.}  We run additional experiments that attempt to isolate the impact of the data advantage and reputation advantage. We find that the data advantage alone still leads to a significant incumbency advantage. Additionally, the data advantage tends to be stronger when the incumbent commits to a more advanced bandit algorithm. Our results highlight the importance of considering competition dynamics when thinking about the anti-trust question of whether data can become a significant barrier to entry in an industry. While data has decreasing returns to scale from a statistical perspective, in a competitive environment the relative differences in the data possessed by the firms may lead to a large competitive benefit due to the feedback loops discussed previously. In our model this effect is amplified when the incumbent commits to a more advanced bandit algorithm since, in the incumbency period, the firm gathers data on possible actions more efficiently leading to the relative gap upon entry to be larger. This is important when exploration can have larger reputational consequences.}

>>>>

\swedit{Beyond the welfare implications, we also investigate the barrier to entry that follows from the incumbent's data advantage.  We run additional experiments that attempt to isolate the impact of the data advantage and reputation advantage. We find that the data advantage from the incumbent's ``small head start'' can lead to a significant incumbency advantage, especially when the incumbent commits to a more advanced bandit algorithm. Our results show that even a small degree of data assymmetry can be amplified to be a larger market advantage through the competition dynamics. This is in contrast to the data advantage in a static environment \cite{varian2018artificial,bajari2018impact}, in which a small amount of additional data can only provide limited improvement in the predictive accuracy. 
Our results shed lights on the importance of considering competition dynamics when reasoning about the anti-trust question of whether data can become a significant barrier to entry in an industry. 
% in a competitive environment the relative differences in the data
% possessed by the firms may lead to a large competitive benefit due
% to the feedback loops discussed previously. In our model this effect
% is amplified when the incumbent commits to a more advanced bandit
% algorithm since, in the incumbency period, the firm gathers data on
% possible actions more efficiently leading to the relative gap upon
% entry to be larger. This is important when exploration can have
% larger reputational consequences.
}}\swcomment{still not super happy about above.}
